Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-02-06 paper/paper.tex
plot and proper Trabelsi citation

% on compresssion
Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
the variational approximation factorizes into univariate distributions, whether a $\cplx$
or $\real$ parameter is zero or not is determined from individual relevance scores $
  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
$: non-zero if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:log-alpha__mnist-like}
displays the general shape of the distribution of $\log \alpha$ on the Fashion-MNIST dataset
in sec.~\ref{sub:mnist_like_datasets}. This shape appears to be typical in every experiment
conducted in this study: there always is a single mode within the moderately negative
range, and one or two modes to the right of zero. The relative mass of each mode changes
with $C$ and the higher the coefficient is, the more mass is shifted to the right. In every
experiment the trough between the peaks of the negative mode and the first positive one
is around zero.

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/kde-histograms-of-log-alpha-distribution.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/kde-histograms-of-log-alpha-distribution.pdf}
  \end{subfigure}
  \caption{%
    Smoothed density of $\log\alpha$ for a convolutional and dense layer from a model
    in sec.~\ref{sub:mnist_like_datasets}.
  }
  \label{fig:log-alpha__mnist-like}
\end{figure}

% on chosing the threshold
The threshold $\tau$ is picked so, that the remaining \textit{``non-zero''} parameters
are within $\delta$ relative tolerance of their mean with high probability under the
approximate posterior $q_\theta(W)$. Since \eqref{eq:c-gauss-vi} is Gaussian, $
  \tfrac{\lvert w - \mu \rvert^2}
        {\alpha \lvert \mu \rvert^2}
$ is $\chi^2_k$ distributed with shape $k=1$ ($\real$) or $2$ ($\cplx$), whence
\begin{equation} \label{eq:prob_relevant}
  \Pr\bigl(
    \lvert w - \mu \rvert \leq \delta \lvert \mu \rvert
  \bigr)
    = \Pr\biggl(
      \frac{\lvert w - \mu \rvert^2}{\alpha \lvert \mu \rvert^2}
        \leq \frac{\delta^2}{\alpha}
    \biggr)
    = \chi^2_k\biggl(\frac{\delta^2}{\alpha}\biggr)
  \,.
\end{equation}
% Figure~\ref{fig:log-alpha__mnist-like} (bottom) shows the probability of a $\real$
% (or $\cplx$)  parameter being non-zero for various $\delta\in(0, \tfrac12)$ as a function
% of $\log \alpha$.
For a reasonably generous $\delta = 25\%$ tolerance all values of $\log \alpha$ below
$-2.5$ yield a relatively high chance of a non-zero parameter. Given that $q_\theta$
is merely an approximation, we opt for a somewhat higher $\log \alpha$ threshold, and
pick $\tau \in [-\tfrac12, \tfrac32]$, which is lower than $\tau = 3$, recommended by
\citet{molchanov_variational_2017}.

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
    \includegraphics[draft,width=1.\linewidth]{../assets/figure__musicnet__trade-off/legacy__musicnetram__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
    \includegraphics[draft,width=1.\linewidth]{../assets/figure__musicnet__threshold/threshold.pdf}
  \end{subfigure}
  \caption{%
    Average Percision frontier for the convolutional model of \citet{trabelsi_deep_2017}.
    Shaded horiontal region represents the $\mu\pm\sigma$ bands for the performance of the
    uncompressed model.
    \textit{top}: Original model ($k=6$) compressed with \textbf{\color{blue} VD}
    (\ref{ssub:variational_dropout}) and \textbf{\color{orange} ARD} (\ref{ssub:empirical_bayes});
    \textit{bottom}: The model of \citet{trabelsi_deep_2017} with kernel size $3$
    compressed with \textbf{\color{blue} VD} (\ref{ssub:variational_dropout}).
  }
  \label{fig:musicnet__trade-off}
\end{figure}

>>>>

% on compresssion
Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
the variational approximation factorizes into univariate distributions, whether a $\cplx$
or $\real$ parameter is zero or not is determined from individual relevance scores $
  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
$: non-zero if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff}
displays the general shape of the distribution of $\log \alpha$ on the Fashion-MNIST dataset
in sec.~\ref{sub:mnist_like_datasets}. This shape appears to be typical in every experiment
conducted in this study: there always is a single mode within the moderately negative
range, and one or two modes to the right of zero. The relative mass of each mode changes
with $C$ and the higher the coefficient is, the more mass is shifted to the right. In every
experiment the trough between the peaks of the negative mode and the first positive one
is around zero.

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/kde-histograms-of-log-alpha-distribution.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__threshold.pdf}
  \end{subfigure}
  \caption{%
    Smoothed density of $\log\alpha$ for a convolutional and dense layer from a model
    in sec.~\ref{sub:mnist_like_datasets}.
  }
  \label{fig:hist__and__threshold__tradeoff}
\end{figure}

% on chosing the threshold
The threshold $\tau$ is picked so, that the remaining \textit{``non-zero''} parameters
are within $\delta$ relative tolerance of their mean with high probability under the
approximate posterior $q_\theta(W)$. Since \eqref{eq:c-gauss-vi} is Gaussian, $
  \tfrac{\lvert w - \mu \rvert^2}
        {\alpha \lvert \mu \rvert^2}
$ is $\chi^2_k$ distributed with shape $k=1$ ($\real$) or $2$ ($\cplx$), whence
\begin{equation} \label{eq:prob_relevant}
  \Pr\bigl(
    \lvert w - \mu \rvert \leq \delta \lvert \mu \rvert
  \bigr)
    = \Pr\biggl(
      \frac{\lvert w - \mu \rvert^2}{\alpha \lvert \mu \rvert^2}
        \leq \frac{\delta^2}{\alpha}
    \biggr)
    = \chi^2_k\biggl(\frac{\delta^2}{\alpha}\biggr)
  \,.
\end{equation}
% Figure~\ref{fig:hist__and__threshold__tradeoff} (bottom) shows the probability of a $\real$
% (or $\cplx$)  parameter being non-zero for various $\delta\in(0, \tfrac12)$ as a function
% of $\log \alpha$.
For a reasonably generous $\delta = 25\%$ tolerance all values of $\log \alpha$ below
$-2.5$ yield a relatively high chance of a non-zero parameter. Given that $q_\theta$
is merely an approximation, we opt for a somewhat higher $\log \alpha$ threshold, and
pick $\tau \in [-\tfrac12, \tfrac32]$, which is lower than $\tau = 3$, recommended by
\citet{molchanov_variational_2017}.

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
    \includegraphics[draft,width=1.\linewidth]{../assets/figure__musicnet__trade-off/legacy__musicnetram__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    Average Percision frontier for the convolutional model of \citet{trabelsi_deep_2017}.
    Shaded horiontal region represents the $\mu\pm\sigma$ bands for the performance of the
    uncompressed model.
    \textit{top}: Original model ($k=6$) compressed with \textbf{\color{blue} VD}
    (\ref{ssub:variational_dropout}) and \textbf{\color{orange} ARD} (\ref{ssub:empirical_bayes});
    \textit{bottom}: The model of \citet{trabelsi_deep_2017} with kernel size $3$
    compressed with \textbf{\color{blue} VD} (\ref{ssub:variational_dropout}).
  }
  \label{fig:musicnet__trade-off}
\end{figure}
